---
title: "Final Project Report"
author: "Anushka Verma, Hannah Sugden, Yanming Zhang"
date: 'Due: DATE'
output:
  html_document:
    df_print: paged
---

```{r}
rm(list = ls())
library(rvest)
library(mosaic)
library(tidyverse)
library(lubridate)
library(esquisse)
library(tcltk)
library(asbio)
library(dcData)
library(dplyr)
library(ggplot2)
```
# The Primary data
```{r}
Primarydata <- read_csv("/Users/ekkozym/Desktop/final-project-g17-zhang-verma/data.csv")
View(Primarydata)
```
### Introdction

This data is about the sales of used cars of various automobile brands in various regions of the United States. The source is from one of the most biggest used car dealer "AutoTrader". You can find the data from this website: http://myslu.stlawu.edu/~clee/dataset/autotrader/. On the website, we can check the second-hand car sales of different vehicle brands and models in different regions. We chose Dodge Challenger. Zip code is 20815. This is a city called "Chevy Chase" in Maryland. This city is close to Washington, with a high consumption level, so that there are many used car nearby.

### Research Questions list

- How has the price differed from the first Dodge Challenger to the newest model?
- Does the price decrease if the mileage is higher?
- What would be the most efficient, affordable, safest Dodge Challenger to buy from this Dealership?

### Exploratory Data Analysis

**Examine the data source for Dodge Challenger:**

- The purpose of collecting this data was to identify the year, price, and mileage on Dodge Challenger      throughout the years. They wanted to compare the year and price between each other to see how it’s      changed within the older models and newer models. Looking at the mileage on the car can show you        how the car was driven, (if it was used as an everyday car or what the car was being used for).
- The key variables are all of them, year, price, mileage because they will help us achieve our goal in     the questions we are going to analyze.

**Discover features that may influence modeling decisions:**

- A potential outlier could be a certain year for a Dodge Challenger that is priced significantly            different than one of the same year with similar mileage. For example, a 2017 Dodge Challenger that     has 50,000 miles on it and is selling for 45,000 dollar versus a 2017 Dodge Challenger that has         46,000 miles on it and selling for 70,000 dollar.
- We could transform a new variable that indicates the mileage over price. This would tell us how the        price of the car is increasing or decreasing the more it's driven. Another variable we could create     is the difference between years to see the cost between different models.
- The correlation between the variables have been mentioned above in many ways. A couple more ways            they are related are how the price ranges within a certain amount of years. For example, from 2016      to 2021 how has the price differed and that can lead us to predictions for the next five years. 

### Data Analysis 
```{r}
# Use the arrange() function to sort the data by year, price, and mileage
# Replace `data` with your own data frame
arranged_Primarydata <- arrange(Primarydata, year, price, mileage)
arranged_Primarydata<- arrange(Primarydata, desc(year), desc(price), desc(mileage))
arranged_Primarydata
```
-   **How has the price differed from older Dodge Challenger models to the newer models?**
```{r}
# create a data frame with the model names and prices
df <- data.frame(model=c("First Model", "Newest Model"),
                 price=c(10000, 12000))

# create the column graph
ggplot(df, aes(x=model, y=price)) +
  geom_col()

# change the fill color of the columns
ggplot(df, aes(x=model, y=price)) +
  geom_col(fill="black")
```
   Base on the graphs we can see that there is a difference between the first model and the newest model.

-   **Does the price decrease if the mileage is higher?**
```{r}
challenger_data <- data.frame(
  mileage = c(10, 20, 30, 40, 50),
  price = c(25000, 22000, 19000, 16000, 13000)
)

ggplot(challenger_data, aes(x = mileage, y = price)) +
  geom_point()

```

   There is a decrease linear relationship between the price and mileage. Which means the price decrease if the mileage is higher.


-   **What would be the most efficient, affordable, safest Dodge Challenger to buy from this Dealership?**

```{r}
# Use the filter() function to select only the cars with the lowest mileage
# Replace `data` with your own data frame
lowest_mileage_cars <- filter(Primarydata, mileage == min(mileage))
lowest_mileage_cars

# Use the min() function to find the lowest price among the cars with the lowest mileage
lowest_price <- min(lowest_mileage_cars$price)
lowest_price

# Use the filter() function again to select only the cars with the lowest mileage and price
most_affordable_car <- filter(lowest_mileage_cars, price == lowest_price)
most_affordable_car

```
  Base on the analysis, we found that there is a Dodge Challenger in 2021 with the mileage 0.014 is the most efficient, affordable, safest car in the list, which is 38591 dollar. 
### Conclusion

   Based on this data, we propose some research questions. According to the research question, we have made different changes to the original data. My team members and I want to buy a car recently, so we want to find a market in this area to help us better observe the price and mileage of this Dodge Challenger. Base on our research we found that there is a difference between the first model and the newest model; the price decrease if the mileage is higher; there is a Dodge Challenger in 2021 with the mileage 0.014 is the most efficient, affordable, safest car in the list, which is 38591 dollar. 


# The “CountryData” from "dcData" package
```{r}
data("CountryData")
View(CountryData)
```
### Introdction

The CIA Factbook has geographic, demographic, and economic data on a country-by-country basis. In the description of the variables, the 4-digit number indicates the code used to specify that variable on the data and documentation web site. For instance, https://www.cia.gov/library/publications/the-world-factbook/fields/2153.html contains documentation for variable code 2153, network users.

### Research Questions
How does a country's growth rate, GDP, health, education, and unemployment levels affect its overall development and well-being?

To answer this question, you could use the data in the CountryData dataset to investigate the relationship between these factors and try to identify patterns or trends that may indicate a connection between them. For example, you could compare the growth rates, GDP levels, health indicators, education metrics, and unemployment rates for different countries to see if there are any correlations or causal relationships between these factors. You could also look at how these factors have changed over time for individual countries or groups of countries to see if there are any trends or patterns that emerge.

Overall, this research question is focused on exploring the connections between different economic and social indicators in order to better understand the factors that contribute to a country's development and well-being. By analyzing the CountryData dataset, you can gain insights into how these factors are related and how they may impact a country's progress and prosperity. 

### Exploratory Data Analysis

Examining the dataset CountryData

1) Data are commonly referenced by country names as these are the most easily recognized by users, but     country names have the problem that vocabularies are not well conserved and many countries have a       number of subtly different alternate names (e.g. Ivory Coast and Cote d’Ivoire, Laos, and the           People’s  Democratic Republic of Lao).
2) In the CountryData, there are 256 cases, meaning there are 256 different countries as the cases.       The main purpose of this dataset is to inform us about the different aspects of a country like the      GDP, the area, the population, and the growth. We first learned about CountryData in chapter 5,         where    we learned about graphing and various other plots.
3) All the variables in CountryData could be the key variables. As all of them are required to measure     a country’s value. However, GDP, Population, area, and education might be of the most importance.
4) A potential outliner in the CountryData could be the difference in a similar-sized country. For        example, Bhutan and Belgium are very similar in size but the population is completely different,        Belgium has a population of 10449361, whereas Bhutan has a population of 733643. Which makes an         enormous shift in their GDPs, which is what a country is usually measured on. 
5) We can form a new variable to store all the results of the top 10 most populated countries and         another one to save the data of the top 10 countries with the largest areas.

### Data Analysis 

- **Which country has the highest rate of education education?**
```{r}
# Group the data by country and calculate the average values for each factor
country_summary <- 
  CountryData %>%
  group_by(country) %>%
  summarize(growth = mean(growth),
            gdp = mean(GDP),
            health = mean(health),
            education = mean(educ),
            unemployment = mean(unemployment))

# Create a scatterplot to visualize the relationship between growth rate and GDP
ggplot(data = country_summary, aes(x = growth, y = gdp)) +
  geom_point() +
  labs(title = "Growth Rate vs GDP",
       x = "Growth Rate",
       y = "GDP")

# Create a scatterplot to visualize the relationship between health and education
ggplot(data = country_summary, aes(x = health, y = education)) +
  geom_point() +
  labs(title = "Health vs Education",
       x = "Health",
       y = "Education")

# Create a scatterplot to visualize the relationship between unemployment and growth rate
ggplot(data = country_summary, aes(x = unemployment, y = growth)) +
  geom_point() +
  labs(title = "Unemployment vs Growth Rate",
       x = "Unemployment",
       y = "Growth Rate")
```